RJObject Paper

### 2014-06-11 Documents/Paper/ms.tex
Paragraphs how I like them
Parskip package
Gaussian likelihood

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

@@

\section{Introduction}
Many inference problems have the following structure. There is some unknown
number, $N$, of objects in a region. Each of the $N$ objects has a property
$x$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a position and a mass).

@@

The model for the signal is
\begin{eqnarray}
y(t) &=& \sum_{i=1}^N A_i \sin \left(\frac{2\pi t}{T_i} + \phi_i\right)
\end{eqnarray}
where there are $N$ sinusoids in the signal, the
amplitudes are $\{A_i\}$, the periods are $\{T_i\}$, and the phases are
$\{\phi_i\}$.

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
\usepackage{parskip}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}

@@

\section{Introduction}
\setlength{\parindent}{0cm}
\setlength{\parskip}{3mm}
Many inference problems have the following structure. There is some unknown
number, $N$, of objects in a region. Each of the $N$ objects has a property
$x$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a position and a mass).

@@

The model for the signal is
\begin{eqnarray}
\mu(t) &=& \sum_{i=1}^N A_i \sin \left(\frac{2\pi t}{T_i} + \phi_i\right)
\end{eqnarray}
where there are $N$ sinusoids in the signal, the
amplitudes are $\{A_i\}$, the periods are $\{T_i\}$, and the phases are
$\{\phi_i\}$.

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point:
\begin{eqnarray}
y_i | N, \{A_i\}, \{T_i\}, \{\phi_i\} \sim
\mathcal{N}\left(\mu(t_i), \sigma^2\right).
\end{eqnarray}
The simulated data is shown in Figure~\ref{fig:sinewave_data}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example.
\label{fig:sinewave_data}}
\end{center}
\end{figure}
